\documentclass[]{neilfoxcroft-resume}


\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN ONE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{minipage}[t]{0.33\textwidth} 
\begin{large}
	\headername{Neil Foxcroft}\\
\end{large}
Bachelor of Science Honours in \\
Computer Science \& Information Technology\\
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     LINKS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Links} 
\noindent\rule{5cm}{0.4pt}

\href{https://github.com/FoxcroftN}{\faGithub} \\
\href{https://www.linkedin.com/in/neilfoxcroft/}{\faLinkedin} \\
\href{http://neilfoxcroft.com/}{\custombold{neilfoxcroft.com}} 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Skills}
\noindent\rule{5cm}{0.4pt}
\subsection{OS}
GNU/Linux, Windows
\vspace{6pt}
\subsection{Languages}
C/C++, Java, Python, javascript
\vspace{6pt}
\subsection{Framework}
Flask, ExtJS, \\Node.js, Android,
Web-development
\vspace{6pt}
\subsection{Databases}
MySQL, PostgreSQL, MangoDB
\vspace{6pt}
\subsection{Others}
Markdown, Git, Vim, \\Sublime Text, Eclipse,\\
Android Studio, Coral Draw,\\
Adobe Illustrator, Photoshop
\sectionsep
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     COURSEWORK
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Coursework}
\noindent\rule{5cm}{0.4pt}

Data Structures\\
Algorithm\\
Neural Networks\\
Discrete Mathematics\\
Operating Systems\\
MySQL\\
Data Analysis
\sectionsep
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Education} 
\noindent\rule{5cm}{0.4pt}\\
\datecolor{20XX-20YY}
\subsection{B.Tech. in CSE}
NIT SRINAGAR \\
CGPA : 8.05/10(Expected)\\
\vspace{8pt}
\datecolor{20XX-20YY}
\subsection{Intermediate}
Hame Convent Inter College, FZD\\
Percentage: 80.8\%\\
\vspace{8pt}
\datecolor{20XX-20YY}
\subsection{High School}
Hame Convent Inter College, FZD\\
Percentage: 81\%
\sectionsep
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN TWO
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{minipage} 
\hfill
\begin{minipage}[t]{0.66\textwidth} 
% \descript{BS in Computer Science}
\hspace*{0pt}\hfill         \\
\hspace*{0pt}\hfill         \\
\hspace*{0pt}\hfill         \\
\hspace*{0pt}\hfill Mobile Number: +27 61 458 9590 \\
\hspace*{0pt}\hfill Email:\space \textbf{\href{mailto:neilfoxcroftpro@gmail.com}{neilfoxcroftpro@gmail.com}} \\
\hspace*{0pt}\hfill Web:\space \textbf{\href{http://neilfoxcroft.com}{http://neilfoxcroft.com}} 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Education
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Education}
\noindent\rule{12.5cm}{0.4pt}
\datecolor{2017-2020} \runsubsection{NWU}
\descript{Bachelors of Science in Information Technology}
\noindent
\hspace{5em}%
\begin{minipage}{0.85\textwidth\vspace{2pt}}
Support of Unit of Measure conversion in istSOS3: My project is to add conversion of
unit of measure in istsos3. User can convert unit in another specified unit.
\end{minipage}
\descriptright{Python, PostgreSQL, Pandas, Numpy, Scipy, Pint, Postgresql-unit, Javascript}
\sectionsep

\datecolor{2021-now} \runsubsection{NWU}
\descript{BSc Honours in Computer Science \& Information Technology}
\noindent
\hspace{5em}%
\begin{minipage}{0.85\textwidth\vspace{2pt}}
Data analysis and statastical tool suit: istsos2 provides easily manage your sensor network
and distribute your data in a standard way. which is be used to automate the creation of statisticate
documents using OAT(Observation analysis tool) and harvesting the data from an istSOS server.
\end{minipage}
\descriptright{ExtJS, Dygraph.js, D3.js, Data analysis, Python, PostGIS, Pandas, Numpy, Scipy}
\sectionsep
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Work Experience
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Work Experience} 
\noindent\rule{12.5cm}{0.4pt}
\datecolor{2017\\NOV-DEC \hspace{0.05cm} } \runsubsection{Platinum Life}
\descript{Sales Agent}
\noindent
\hspace{5em}%
\begin{minipage}{0.85\textwidth\vspace{2pt}}
Learned to work in a highly competitive environment. Completed the sales training course and worked as a sales representative.
\end{minipage}
\datecolor{2019\\JUL \hspace{1.04cm}} \runsubsection{Fulcrum}
\descript{Student Intern}
\noindent
\hspace{5em}%
\begin{minipage}{0.85\textwidth\vspace{2pt}}
Experienced the work routine of an IT professional and received mentorship on how to approach IT-related work problems.
\end{minipage}
\datecolor{2021\\FEB-DEC \hspace{0.25cm}} \runsubsection{NWU}
\descript{Tutor \& Assistant}
\noindent
\hspace{5em}%
\begin{minipage}{0.85\textwidth\vspace{2pt}}
Assisted in practical training of undergrad's in the final year networks module (CMPG 315) for the IT degree. Helped with feedback regarding assignments in the module and aided in the understanding of required practical software (CISCO Packet Tracer)
\end{minipage}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SIDE PROJECT
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Side Project}
\noindent\rule{12.5cm}{0.4pt}
\datecolor{20XX-now} \runsubsection{Digital Certificate Dapp using Ethereum}
\descript{Blockchain, Web3JS}
\noindent
\hspace{5em}%
\begin{minipage}{0.85\textwidth\vspace{5pt}}
A Dapp issue certificate and verify. An Idea to use Blockchain to create Digital Certificate.
\end{minipage}
\datecolor{20XX-now} \runsubsection{Identifying Gender From Images of Faces}
\descript{ML}
\noindent
\hspace{5em}%
\begin{minipage}{0.85\textwidth\vspace{5pt}}
Identifying gender of a person by looking at his/her Photograph.
\end{minipage}
\datecolor{20XX-now} \runsubsection{Small Project}
\descript{Android, Data Analysis, Image Processing}
\noindent
\hspace{5em}%
\begin{minipage}{0.85\textwidth\vspace{5pt}}
Result Portal, Voice Calci, Cubic Bispline, Image Compression, smoothing, Fitting Curve.
\end{minipage}
\end{minipage} 
\end{document}  \documentclass[]{article}